---
title: "R Notebook"
output: html_notebook
---

#load in libraries to be used
library(tidyverse)
library(here)
library(janitor)

#test where the top level of the project directory is 
here::here()

#use this to set the path to the data file
raw_data <- read_( here(""))

#assign raw data and apply janitor to clean names 
result_table <- clean_names(raw_data)

names(result_table)

#no column for name - must be a row name perhaps

row.names(result_table)

rt_name <- rownames_to_column(result_table, var="name") 

summary(rt_name)

```{r}
#load in libraries to be used
library(tidyverse)
library(here)
library(janitor)
library(readxl)

#test where the top level of the project directory is 
here::here()

#use this to set the path to the data file
raw1 <- read_xlsx(here("raw_data/boing-boing-candy-2015.xlsx"))

raw2 <- read_xlsx( here("raw_data/boing-boing-candy-2016.xlsx"))

raw3 <- read_xlsx( here("raw_data/boing-boing-candy-2017.xlsx"))
#assign raw data and apply janitor to clean names 

glimpse(raw1)
summary(raw1)

#how to chnage all the column headers at once
colnames(object) <- sub("Log\\.", "", colnames(object))

colnames(df) <- gsub('.', '', colnames(df), fixed=TRUE)
```

```{r}
raw3 %>% 
  group_by(`Q4: COUNTRY`) %>% 
  mutate(count = n(), .after = `Q4: COUNTRY`) %>% 
  select(`Q4: COUNTRY`, count)
  


```

```{r}
clean_names(raw3)
```

