---
title: "R Notebook"
output: html_notebook
---

```{r}

#load in libraries to be used
library(tidyverse)
library(here)
library(janitor)

#test where the top level of the project directory is 
here::here()


#use this to set the path to the data file
raw_data <- read_rds( here("raw_data/decathlon.rds"))

#assign raw data and apply janitor to clean names 
result_table <- clean_names(raw_data)

names(result_table)

#no column for name - must be a row name perhaps

row.names(result_table)

rt_name <- rownames_to_column(result_table, var="name") 

summary(rt_name)
```
From the summary of the data it can be seen that there are 2 competitions with 10 events, rank and points 



```{r}
class(rt_name$long_jump
    )
#mutate the columns to lowercase 
rt_name %>% 
   mutate_all(.funs = tolower)
```



```{r}

#to make into a long form table

 
long_form_data <- rt_name %>%
    pivot_longer(
    cols = c(x100m, long_jump, shot_put, high_jump, x400m, x110m_hurdle, discus, pole_vault, javeline, x1500m),
    names_to = "event",
    values_to = "results"
    ) %>% 
  mutate_all(.funs=tolower) %>% 
  mutate_at(vars(points, rank, results), as.numeric)
  
long_form_data
```

Who had the longest long jump seen in the data?
```{r}
long_form_data %>% 
  group_by(event) %>% 
  filter(event == "long_jump") %>% 
  arrange(desc(results)) %>% 
  head(1)
```


What was the average 100m time in each competition?

```{r}
long_form_data %>% 
  filter(event == "x100m") %>% 
  group_by(competition) %>% 
  summarise(avg_time = mean(results, na.rm = TRUE))

```
Who had the highest total points across both competitions?

```{r}
long_form_data %>% 
  select(name, points) %>% 
  arrange(desc(points)) %>% 
  head(1)
  
 
```

What was the shot-put scores for the top three competitors in each competition?



```{r}
long_form_data %>% 
  arrange(desc(points)) %>% 
  filter(event == "shot_put", competition == "olympicg") %>% 
  head(3)

```

```{r}
long_form_data %>% 
  arrange(desc(points)) %>% 
  filter(event == "shot_put", competition == "decastar") %>% 
  head(3)
```
What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

```{r}


less_than_50 <- long_form_data %>% 
  arrange(desc(points)) %>% 
  filter(event == "x400m", results <= 50)

  mean(less_than_50$points)





# mutate(avg_points = mean(less_than_50))
# avg_points

  # mutate(avg_points = mean(long_form_data %>% 
  #  mutate_at(vars(points, rank), as.numeric) %>% 
  # arrange(desc(points)) %>% 
  # filter(event == "x400m", results<= "50")))
```

```{r}
greater_than_50 <- long_form_data %>% 
  arrange(desc(points)) %>% 
  filter(event == "x400m", results >= 50)

  mean(greater_than_50$points)
```

